---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# roam

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/roam)](https://CRAN.R-project.org/package=roam)
[![R build status](https://github.com/mitchelloharawild/roam/workflows/R-CMD-check/badge.svg)](https://github.com/mitchelloharawild/roam)
<!-- badges: end -->

The roam package allows you to include larger datasets (and other objects) in packages without increasing installation size (and exceeding CRAN size limits). How? With *Remote Object ActiveBinding Magic* (roam).

Using active bindings, the familiar interface for package datasets is retained. When an object/dataset is accessed for the first time, the user is prompted to download the object into an app directory for caching. Any subsequent time it is accessed, it returns the object as normal.

## Installation

<!-- You can install the released version of roam from [CRAN](https://CRAN.R-project.org) with: -->

<!-- ``` r -->
<!-- install.packages("roam") -->
<!-- ``` -->

The **development** version can be installed from GitHub using:

```{r gh-installation, eval = FALSE}
# install.packages("remotes")
remotes::install_github("mitchelloharawild/roam")
```

## Example

None yet.
